---
title: "CLT_WUP"
author: "Adam Ayala"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

kkardashtemp  see code below

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")

my1000 <- sample(Homers_data , size = 1000, replace=T)

```

```{r}

library(ggplot2)
sampleNumber = sample(1:10000, size = 1000)
library(dplyr)
my1000 <- Homers_data[sampleNumber, ]
names(my1000)
# Basic density
p <- ggplot(my1000, aes(x=kkardashtemp,col=sex)) + 
  geom_density()
p
# Add mean line
p+ geom_vline(aes(xintercept=mean(kkardashtemp)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$kkardashtemp),' sd = ',sd(my1000$kkardashtemp)))
```

```{r}
numb=2
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k2 = x.avg

p <- ggplot(my1000, aes(x=k2)) + 
  geom_density() 
p

# Add mean line
  geom_vline(aes(xintercept=mean(k2)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$k2),' sd = ',sd(my1000$k2)))

```

 

```{r}
numb=9
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k9 = x.avg

p <- ggplot(my1000, aes(x=k9), (Col=sex))+
geom_density()

# Add mean line
geom_vline(aes(xintercept=mean(k9)),
color="blue", linetype="dashed", size=1)
p + ggtitle("n = 9") +
xlab("temperature") + ylab("desnity")

print(paste('mean = ', mean(my1000$k9),' sd = ',sd(my1000$k9)))

```

The mean will always get close to 50 and the standard deviation is getting smaller. This makes sense since the dividing number in the standard deviation formula is getting bigger, when we predict using 41.38 as the sample standard deviation and use sqrt(9) as the sample size we see the predicted value to be 13.79333 and this is pretty close to the approximate value of 14 for the standard deviation.
